\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}

### 2020-03-17 docs/paper/paper.tex
fix: doc

Machine Learning (ML) techniques are coming to the forefront of many fields, surpassing the human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology. Artificial Neural Networks can approximate any function by virtue of the Universality theorem: No matter what the input is there is to be a guaranteed ANN architecture that computes the desired outputs. This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures [1], optimization of photonic crystal nanocavities [2], and more recently, computing optical properties of a photonic crystal fiber [3].

@@

We will first train ANN model to predict the confinement loss of a SPR based PCF using the original data set collected. Then we will augment the original training data set with generated samples by the GAN, to improve the performance of the ANN model.
Previous works [10, 11], demonstrated that random data augmentation actually had weakened the performance of the model. Hence, active researches are ongoing to find ways to optimally sample the generated data [12], in other words to filter out the "good" generated data after training the GAN. In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss. In the following sub-sections we discuss the networks architectures. Before we proceed, it is worth mentioning that the choices made for the parameters of the networks are by no means a robust set of rules, rather, they are rules of thumb and heuristics, as no such rules have been yet developed for ANN models.

@@

A labelled data set of only 432 samples was collected in this work, through simulations using FV-FEM. This length of the data set made the task of building ANN model look quiet impossible, however the results were satisfying to some extent. This data set consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables. The labels are the confinement loss of the PCF. The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for three different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36) [35]). Seven configurations were randomly selected for training both the WGAN-GP and the ANN, one configuration was held out for validation, and the last configuration for testing. This data was preprocessed before fed in the networks. The indices of refraction  are very close, which made it quiet difficult for the neural networks to differentiate between them, after many trials, the best choice was to take only the tens digit of ${134, 135, 136}$, giving ${4, 5, 6}$. Finally, we transform the confinement loss to the log scale, for the purpose of shortening the distance between the confinement loss points

@@

\newpage
The MSE on the training sets ranged from 0.0030 to 0.0050. For all training data sets the MSE decreased in an acceptable manner. Next, we plot the predictions the ANN model made after training using only the original. As shown in the following figure data-set.

@@

\hspace{-0.07\textwidth}
\begin{figure}[h]
    \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			xlabel=$Epochs$, 
			ylabel=$ Training $ $ MSE $,
			title={Training loss function of the Critic network},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[line width=1pt,solid,color=blue]  %
			table{wgan_tr_loss.txt};
			\end{axis}
			\end{tikzpicture}
\end{subfigure}\hspace{0.05\textwidth}
    \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 1000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_1000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 2000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_2000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}\hspace{0.05\textwidth}
\begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 3000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_3000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
\caption{}
\end{figure}
\newpage
It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in Figure(num).

\begin{figure}
    \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			title={$n_{analyte=1.33}$},
			xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table[x={X},y={Y_REAL}]{133.txt};
			\addlegendentry{$Actual$}
			\addplot[smooth, 
			line width=1pt,solid,color=blue]  %
			table[x={X},y={Predictions}]{133.txt};
			\addlegendentry{$Predictions$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}\hspace{0.05\textwidth}
 \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			title={$n_{analyte=1.34}$},
			xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table[x={X},y={Y_REAL}]{134.txt};
			\addlegendentry{$Actual$}
			\addplot[smooth,
			line width=1pt,solid,color=blue]  %
			table[x={X},y={Predictions}]{134.txt};
			\addlegendentry{$Predictions$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
 \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			title={$n_{analyte=1.35}$},
		    xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table[x={X},y={Y_REAL}]{135.txt};
			\addlegendentry{$Actual$}
			\addplot[smooth,line width=1pt,solid,color=blue]  %
			table[x={X},y={Predictions}]{135.txt};
			\addlegendentry{$Predictions$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
\caption{}
\end{figure}
\newpage
\subsection{Computational performance}

@@

Next, we compare the testing runtime of the ANN model to that of simulation methods used to compute the confinement loss for 3 different analytes and 16 wavelenghts, i.e a total of 48 values of the confinement loss, demonstrated in Table(num). This result is absolutely staggering. The ANN model calculated 16 confinement losses in just 0.17 seconds, while simulations took about 2 hours. Therefore, a well trained ANN model can be used to accurately find the best PCF geometric properties set that maximisez the distance between the confinement loss distributions of each analyte in a matter of seconds to minutes. Hence, accelerate the search for the best PCF sensor.

>>>>

Machine Learning (ML) techniques are coming to the forefront of many fields, surpassing human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology. Artificial Neural Networks can approximate any function by virtue of the Universality theorem: No matter what the input is there is to be a guaranteed ANN architecture that computes the desired outputs. This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures [1], optimization of photonic crystal nanocavities [2], and more recently, computing optical properties of a photonic crystal fiber [3].

@@

We will first train ANN model to predict the confinement loss of a SPR based PCF using the original data set collected. Then we will augment the original training data set with generated samples by the GAN, to improve the performance of the ANN model.
Previous works [10, 11], demonstrated that random data augmentation actually had weakened the performance of the model. Hence, active researches are ongoing to find ways to optimally sample the generated data [12], in other words to filter out the "good" generated data after training the GAN. In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables, and the confinement loss. In the following sub-sections we discuss the networks architectures. Before we proceed, it is worth mentioning that the choices made for the parameters of the networks are by no means a robust set of rules, rather, they are rules of thumb and heuristics, as no such rules have been yet developed for ANN models.

@@

A labelled data set of only 432 samples was collected in this work, through simulations using FV-FEM. This length of the data set made the task of building ANN model look quiet impossible, however the results were satisfying to some extent. This data set consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables. The labels are the confinement loss of the PCF. The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for three different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36) [35]). Seven configurations were randomly selected for training both the WGAN-GP and the ANN, one configuration was held out for validation, and the last configuration for testing. This data was preprocessed before fed in the networks. The indices of refraction  are very close, which made it quiet difficult for the neural networks to differentiate between them, after many trials, the best choice was to take only the tens digit of ${134, 135, 136}$, giving ${4, 5, 6}$. Finally, we transform the confinement loss to the log scale, for the purpose of shortening the distances between the confinement loss points.

@@

\newpage
The MSE on the training sets ranged from 0.0030 to 0.0050. For all training data sets the MSE decreased in an acceptable manner. Next, we plot the predictions the ANN model made on the test set, after training using only the original set. As shown in the following figure.

@@

\hspace{-0.07\textwidth}
\begin{figure}[h]
    \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			xlabel=$Epochs$, 
			ylabel=$ Training $ $ MSE $,
			title={Training loss function of the Critic network},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[line width=1pt,solid,color=blue]  %
			table{wgan_tr_loss.txt};
			\end{axis}
			\end{tikzpicture}
\end{subfigure}\hspace{0.05\textwidth}
    \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 1000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_1000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 2000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_2000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}\hspace{0.05\textwidth}
\begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 3000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_3000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
\caption{}
\end{figure}
It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in Figure(num).
The most important result in these experiments is that the ANN model predicted the correct location of the peak value of the confinement loss distributions for the three different analytes used. 
\begin{figure}
    \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			title={$n_{analyte=1.33}$},
			xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table[x={X},y={Y_REAL}]{133.txt};
			\addlegendentry{$Actual$}
			\addplot[smooth, 
			line width=1pt,solid,color=blue]  %
			table[x={X},y={Predictions}]{133.txt};
			\addlegendentry{$Predictions$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}\hspace{0.05\textwidth}
 \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			title={$n_{analyte=1.34}$},
			xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table[x={X},y={Y_REAL}]{134.txt};
			\addlegendentry{$Actual$}
			\addplot[smooth,
			line width=1pt,solid,color=blue]  %
			table[x={X},y={Predictions}]{134.txt};
			\addlegendentry{$Predictions$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
 \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			title={$n_{analyte=1.35}$},
		    xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table[x={X},y={Y_REAL}]{135.txt};
			\addlegendentry{$Actual$}
			\addplot[smooth,line width=1pt,solid,color=blue]  %
			table[x={X},y={Predictions}]{135.txt};
			\addlegendentry{$Predictions$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
\caption{}
\end{figure}
\subsection{Computational performance}

@@

Next, we compare the testing runtime of the ANN model to that of simulation methods used to compute the confinement loss for 3 different analytes and 16 wavelenghts, i.e a total of 48 values of the confinement loss, demonstrated in Table(num). This result is absolutely staggering. The ANN model calculated 48 confinement losses in just 0.17 seconds, while simulations took about 2 hours. Therefore, a well trained ANN model can be used to accurately find the best PCF geometric properties set that maximisez the distance between the confinement loss distributions of each analyte in a matter of seconds to minutes. Hence, accelerate the search for the best PCF sensor.
